Dynamic Slice Backsolving

### 2014-03-20 docs/paper/fsuthesis/thesis-template/paper.tex
moved abstract to intro, made new abstract, nice and short

\title{A Survey of Fuzzing and New Technique for Dynamic Analysis}
\author{Clark Wood}
\college{College of Arts and Science}
\department{Department of Computer Science} % Delete if no department
\manuscripttype{Thesis}              % [Thesis, Dissertation, Treatise]
\degree{Masters of Science}                 
\semester{Spring}                            % [Spring, Summer, Fall]
\degreeyear{2014}
\defensedate{XXXXXXX}

@@

@@

>>>>

\title{Dynamic Slice Backsolving}
%\title{A Survey of Fuzzing and New Technique for Dynamic Analysis}
\author{Clark Wood}
\college{College of Arts and Science}
\department{Department of Computer Science} % Delete if no department
\manuscripttype{Thesis}              % [Thesis, Dissertation, Treatise]
\degree{Masters of Science}                 
\semester{Spring}                            % [Spring, Summer, Fall]
\degreeyear{2014}
\defensedate{XXXXXXX}

@@

Finding bugs in software is a difficult but lucrative endeavour. Fuzzing is one technique for finding bugs, particularly exploitable vulnerabilities, employed by both software companies and nation-state actors. When no source code is available, fuzzing complex programs can prove difficult, and as techniques become more sophisticated they require more resources and time. We present a technique, dynamic slice backsolving, which, to the best of our knowledge, represents a novel way to reason about not only the location of user input bytes which contribute to interesting program behavior like branching, but also the exact byte value necessary to trigger a desire branch condition. We have implemented this technique in a fuzzer, which is able to reason about large and complex user input and reliably drive program execution down new code paths to explore new portions of compiled code.

@@

We have implemented this technique in a proof of concept fuzzer, stubble, which operates on x86 binaries. Stubble requires no access to source code, unlike many fuzzers utilizing symbolic execution, and automatically generates test files which exercise new paths in the input program. Program input, output, and interesting conditions like segfaults are recorded during execution, and taint propagation is recorded from user input sources to branch sinks. When a tainted branch is found, stubble automically backsolves the execution slice and generates a new test case which will drive the program down the opposite path explored in the current execution. Stubble is able to reason about hundreds of bytes of user input, for instance by performing oracle attacks on binaries which check user input against large secrets, requiring O(n) test cases to solve the secret with no previous information, where n is length of the secret. Stubble has also been parallized at the process level, allowing for an arbitrary number of independent bytes to be reasoned about concurrently. We believe dynamic slice backsolving is a reasonable complementary technique to dynamic taint analysis and symbolic execution for binary fuzzing.
